|

### 2022-12-29 paper.Rmd
Wed Dec 28 22:00:05 CET 2022: update-remote.sh
Thu Dec 29 20:00:08 CET 2022: update-remote.sh

```{bash ipythonRunner, include=FALSE}

# Set the base directory
EXPDIR="/Users/rmn/masterThesis/eda-gp-2020"

@@

DAE-GP builds upon the concept of using DAEs in EDAs described by @harmless_overfitting_eda and transfers the concept to the domain of GP. 
The mutation and crossover operators of standard GP are replaced by sampling new solutions from a probabilistic model that is build by training a DAEs long short-term memory (LSTM) network on a subset of high fitness solutions from the current population [@dae-gp_2020_rtree]. 
LSTMs are a variant of recurrent neural networks first introduced by @lstm_orig that can store learned information over en extended time period while avoiding the problem of vanishing and/or exploding gradients. Since DAE-GP encodes candidate solutions as linear strings in prefix notation, the DAE in DAE-GP uses LSTMs for both encoding and decoding where the total amount of time steps $T$ is equal to sum of the length of the input solution and the output solution [@dae-gp_2020_rtree].

@@

The DAE-GP algorithm, first described by @dae-gp_2020_rtree, is described by algorithm 1

```{.numberLines}
WHILE NOT termination_criterion
  DO 
END WHILE
RETURN
```

@@

```{python load_MWU_ include=FALSE}
from json import load

S = load(open("./data/airfoil_FullRun_30gens/MWU-BestFitnessByGen.json", "r", encoding="utf-8"))
statistic_mwu_fitness = S["statistic"]
pval_mwu_fitness = round(S["p-value"], 4)
print(pval_mwu_fitness)

````
The result of the MWU test is `r py$pval_mwu_fitness`!

>>>>

```{bash ipythonRunner, include=FALSE}
# Set the base directory
EXPDIR="/Users/rmn/masterThesis/eda-gp-2020"

@@

DAE-GP builds upon the concept of using DAEs in EDAs described by @harmless_overfitting_eda and transfers the concept to the domain of GP. 
The mutation and crossover operators of standard GP are replaced by sampling new solutions from a probabilistic model that is build by training a DAEs long short-term memory (LSTM) network on a subset of high fitness solutions from the current population [@dae-gp_2020_rtree].

LSTMs are a variant of recurrent neural networks first introduced by @lstm_orig that can store learned information over en extended time period while avoiding the problem of vanishing and/or exploding gradients. Since DAE-GP encodes candidate solutions as linear strings in prefix notation, the DAE in DAE-GP uses LSTMs for both encoding and decoding where the total amount of time steps $T$ is equal to sum of the length of the input solution and the output solution [@dae-gp_2020_rtree].

@@

The DAE-GP algorithm, first described by @dae-gp_2020_rtree, is summarized by chart 1.

![DAE-GP - Flowchart](./img/flowcharts/dae-gp.png)

@@

```{python, load_MWU, include=FALSE}
from json import load

S = load(open("./data/airfoil_FullRun_30gens/MWU-BestFitnessByGen.json", "r", encoding="utf-8"))
statistic_mwu_fitness = S["statistic"]
pval_mwu_fitness = round(S["p-value"], 4)
print(pval_mwu_fitness)
```

The result of the MWU test is `r py$pval_mwu_fitness`
